A02 - Resilience index

### 2019-01-03 A02-Resilience.Rmd
Draft 0.1.9011 JC and CP review except discussion last paragraph

```{r IrGraph1, eval=F, include=F}
mature %>% 
  select(time, sim, agb) %>% 
  separate(sim, c("SR", "CVH"), remove = F) %>% 
  mutate(disturbance = 50) %>% 
  rbind(ecosystem %>% 
          select(time, sim, agb) %>% 
          separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
  filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
  mutate(agb = agb/10^3) %>% 
  reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
  rename(control = `0`, treatment = `50`) %>% 
  ggplot(aes(x = time)) +
  geom_line(aes(y = control, color = "control")) +
  geom_line(aes(y = treatment, color = "disturbed")) +
  geom_ribbon(aes(ymax = control, ymin = treatment), 
              fill = "lightgrey", col = NA, alpha = 0.5) +
  xlab("Time (years)") +
  ylab("Aboveground biomass (tonC/ha)") +
  scale_color_discrete("Disturbance\nintensity\n(% of BA)", 
                       labels = c("0 (control)", "50 (disturbed)")) +
  ggsave(filename = "./images/original1.png", width = 20, height = 10, units = "cm")
```

```{r IrGraph2, eval=F, include=F}
bind_rows(
  mature %>% 
    select(time, sim, agb) %>% 
    separate(sim, c("SR", "CVH"), remove = F) %>% 
    mutate(disturbance = 50) %>% 
    rbind(ecosystem %>% 
            select(time, sim, agb) %>% 
            separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
    filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
    mutate(agb = agb/10^3) %>% 
    reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
    rename(control = `0`, treatment = `50`) %>% 
    mutate(control = ifelse(is.na(control), treatment, control)) %>% 
    mutate(type = "Raw"),
  mature %>% 
    select(time, sim, agb) %>% 
    separate(sim, c("SR", "CVH"), remove = F) %>% 
    mutate(disturbance = 50) %>% 
    rbind(ecosystem %>% 
            select(time, sim, agb) %>% 
            separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
    filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
    mutate(agb = agb/10^3) %>% 
    reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
    rename(control = `0`, treatment = `50`) %>% 
    mutate(control = ifelse(is.na(control), treatment, control)) %>% 
    mutate(treatment = treatment/control) %>% 
    mutate(control = control/control) %>%
    mutate(type = 'Normalized by control')
) %>% 
  mutate(type = factor(type, levels=c('Raw', 'Normalized by control'))) %>% 
  ggplot(aes(x = time)) +
  geom_line(aes(y = control, color = "control")) +
  geom_line(aes(y = treatment, color = "disturbed")) +
  geom_ribbon(aes(ymax = control, ymin = treatment), 
              fill = "lightgrey", col = NA, alpha = 0.5) +
  xlab("Time (years)") +
  ylab("Aboveground biomass (tonC/ha)") +
  scale_color_discrete("Disturbance\nintensity\n(% of BA)", 
                       labels = c("0 (control)", "50 (disturbed)")) +
  facet_wrap(~type, nrow = 2, scales = "free") +
  ggsave(filename = "./images/original2.png", width = 20, height = 20, units = "cm")
```

>>>>

```{r IrGraph1, eval=F, include=F}
mature %>% 
  select(time, sim, agb) %>% 
  separate(sim, c("SR", "CVH"), remove = F) %>% 
  mutate(disturbance = 50) %>% 
  rbind(ecosystem %>% 
          select(time, sim, agb) %>% 
          separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
  filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
  mutate(agb = agb/10^3) %>% 
  reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
  rename(control = `0`, treatment = `50`) %>% 
  ggplot(aes(x = time)) +
  geom_line(aes(y = control, color = "control")) +
  geom_line(aes(y = treatment, color = "disturbed")) +
  geom_ribbon(aes(ymax = control, ymin = treatment), 
              fill = "lightgrey", col = NA, alpha = 0.5) +
  xlab("Time (years)") +
  ylab("Aboveground biomass (tonC/ha)") +
  scale_color_discrete("Disturbance\nintensity\n(% of BA)", 
                       labels = c("0 (control)", "50 (disturbed)")) #+
  # ggsave(filename = "./images/original1.png", width = 20, height = 10, units = "cm")
```

```{r IrGraph2, eval=F, include=F}
bind_rows(
  mature %>% 
    select(time, sim, agb) %>% 
    separate(sim, c("SR", "CVH"), remove = F) %>% 
    mutate(disturbance = 50) %>% 
    rbind(ecosystem %>% 
            select(time, sim, agb) %>% 
            separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
    filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
    mutate(agb = agb/10^3) %>% 
    reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
    rename(control = `0`, treatment = `50`) %>% 
    mutate(control = ifelse(is.na(control), treatment, control)) %>% 
    mutate(type = "Above-ground biomass (MgC/ha)"),
  mature %>% 
    select(time, sim, agb) %>% 
    separate(sim, c("SR", "CVH"), remove = F) %>% 
    mutate(disturbance = 50) %>% 
    rbind(ecosystem %>% 
            select(time, sim, agb) %>% 
            separate(sim, c("SR", "CVH", "disturbance"), remove = F)) %>% 
    filter(SR == 25, CVH == 4, disturbance %in% c(0, 50)) %>% 
    mutate(agb = agb/10^3) %>% 
    reshape2::dcast(time ~ disturbance, value.var = "agb") %>% 
    rename(control = `0`, treatment = `50`) %>% 
    mutate(control = ifelse(is.na(control), treatment, control)) %>% 
    mutate(treatment = treatment/control) %>% 
    mutate(control = control/control) %>%
    mutate(type = 'AGB recovery')
) %>%
  ggplot(aes(x = time)) +
  geom_line(aes(y = control, color = "control")) +
  geom_line(aes(y = treatment, color = "disturbed")) +
  geom_ribbon(aes(ymax = control, ymin = treatment), 
              fill = "lightgrey", col = NA, alpha = 0.5) +
  xlab("Time (years)") +
  ylab("") +
  scale_color_discrete("Disturbance\nintensity\n(% of BA)", 
                       labels = c("0 (control)", "50 (disturbed)")) +
  facet_wrap(~type, nrow = 2, scales = "free") +
  ggsave(filename = "./images/original2.png", width = 20, height = 20, units = "cm")
```
